Quantifying uncertainty in Pareto estimates of global lake area

### 2021-10-06 manuscript/manuscript.tex
censored predictions match hydrolakes finally
update title
cleanup
frequentist table placeholder

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
%\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{lipsum}		% Can be removed after putting your text content
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{doi}
\usepackage{listings}

\title{Quantifying uncertainty in Pareto lake area estimates}

%\date{September 9, 1985}	% Here you can change the date presented in the paper title
%\date{} 					% Or removing it

@@

Visual inspection of the frequentist method of computing on the edf appeared to produce a reasonable density estimate for small censored lakes (Figure \ref{fig:predict_area}). In addition, estimates of total lake area are somewhat close to the "true" value (Table \ref{tab:pred_table}). However, uncertainty around the frequentist estimates is unrealistically small (Figure \ref{fig:frequentist_uncertainty}).

\begin{figure}
	\centering
	\includegraphics{figures/predict_area-1}
	\caption{Censored lake area edf (solid line) and cdf estimate (dashed line).}
	\label{fig:predict_area}
\end{figure}

\begin{figure}
	\centering
	\includegraphics{figures/frequentist_uncertainty-1}
	\caption{Confidence interval of frequentist density predictions for censored data (the dashed portion in Figure 2. The confidence interval here has essentially no width.}
	\label{fig:frequentist_uncertainty}
\end{figure}

@@

I have shown that the typical frequentist cutoff method produces reasonable estimates of the density of small censored lakes but that it does not capture uncertainty in total lake area (Table \ref{tab:pred_table}, Figure \ref{fig:frequentist_uncertainty}). Furthermore, I have shown that models fit using a Bayesian approach indicate substantial uncertainty in both total lake area and the underlying Pareto shape parameter $a$ used to derive these estimates (Figure \ref{fig:bayesian_model}, \ref{fig:bayesian_area}).

>>>>

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
%\usepackage{nicefrac}      % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{doi}
\usepackage{listings}

\title{Quantifying uncertainty in Pareto estimates of global lake area}

%\date{September 9, 1985}	% Here you can change the date presented in the paper title
\date{} 					% Or removing it

@@

Visual inspection of the frequentist method of computing on the edf appeared to produce a reasonable density estimate for small censored lakes (Figure \ref{fig:predict_area}). In addition, estimates of total lake area are somewhat close to the "true" value (Table \ref{tab:pred_table}). However, uncertainty around the frequentist estimates is unrealistically small (Figure \ref{tab:frequentist_uncertainty}).

\begin{figure}
	\centering
	\includegraphics{figures/predict_censor-1}
	\caption{Censored lake area edf (solid line) and cdf estimate (dashed line).}
	\label{fig:predict_censor}
\end{figure}

% \begin{figure}
% 	\centering
% 	\includegraphics{figures/frequentist_uncertainty-1}
% 	\caption{Confidence interval of frequentist density predictions for censored data (the dashed portion in Figure 2. The confidence interval here has essentially no width.}
% 	\label{tab:frequentist_uncertainty}
% \end{figure}
\begin{table}
	\caption{Frequentist uncertainty}
	\centering
	\begin{tabular}{ccc}
		\toprule
		Q5 ($km^2$) & Q50 ($km^2$) & Q95 ($km^2$) \\
		\midrule
		2.271e+05          & 2.263e+05   & 123     \\
		\bottomrule
	\end{tabular}
	\label{tab:frequentist_uncertainty}
\end{table}

@@

I have shown that the typical frequentist cutoff method produces reasonable estimates of the density of small censored lakes but that it does not capture uncertainty in total lake area (Table \ref{tab:pred_table}, Figure \ref{tab:frequentist_uncertainty}). Furthermore, I have shown that models fit using a Bayesian approach indicate substantial uncertainty in both total lake area and the underlying Pareto shape parameter $a$ used to derive these estimates (Figure \ref{fig:bayesian_model}, \ref{fig:bayesian_area}).
